Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-08-17 manuscript/bef_stability/appendix.Rmd

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)

@@

```{r, echo = FALSE}
package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
purrr::map_(package, ~ toBibtex(citation(.x)))

@@

#### Obtain network of a community

The trophic network of a community (i.e. one network for each fish community
sampling) was obtained by determining the trophic species of each fish
individual in the community and interactions were set according to the metaweb.
All the resource nodes were assumed to be present in each local network.
Finally, the structure of the local networks varied according the presence of
the trophic species. The inferred interactions represent potential interactions
(i.e. not measured interactions) and are binary (i.e. presence or absence of
feeding interactions).

@@

```{r, fig.height = 20/2.54}
pca_pressure <- habitat_press
myload(fourier, dir = mypath("data-raw", "polluants"))
myload(flow_temp_metrics, dir = mypath("data"))
sf_pressure <- station_analysis %>% 
  select(id) %>%
  left_join(rename(pca_pressure, id = station)) %>%
  na.omit()

@@

>>>>

knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)

@@

```{r, echo = FALSE}
package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
purrr::map(package, ~ toBibtex(citation(.x)))

@@

#### Local trophic network

The local trophic network (i.e. one network for each fish community
sampling) was obtained by determining the trophic species of each fish
individual in the community and interactions were set according to the metaweb.
All the resource nodes were assumed to be present in each local network.
Finally, the structure of the local networks varied according the presence of
the trophic species. The inferred interactions represent potential interactions
(i.e. not measured interactions) and are binary (i.e. presence or absence of
feeding interactions).

@@

```{r, fig.height = 20/2.54}
pca_pressure <- habitat_press
myload(fourier, dir = mypath("data-raw", "polluants"))
myload(flow_temp_metrics, station_analysis, the_8_hydrologic_basin, dir = mypath("data"))
sf_pressure <- station_analysis %>% 
  select(id) %>%
  left_join(rename(pca_pressure, id = station)) %>%
  na.omit()

@@

# Species list and food diet data

```{r sp-list}
myload(species, fish_diet_shift, dir = mypath("data"))
kable(species,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = "Fish species list."
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))

```{r food}
kable(fish_diet_shift,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = "Ontogenic diet shift for each species"
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))

### 2020-08-17 manuscript/bef_stability/manuscript.Rmd

---
title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, (Willem Bonnaffe ici?), Elisa Thebault and Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    toc: false 
    fig_caption: true 
    keep_tex: true
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

@@

- Number of words:
  - Abstract: 208 
  - Main text: XXXX

- Number of references: XXX
- Number of figures: 2
- Number of tables: 2
- Number of text boxes: 0

- Coresponding author:
  - Alain Danet
  - UMR 7204 CESCO, BP 61; 45, rue Buffon, 75005 Paris, France
  - alain.danet@mnhn.fr 
  - +331XXXXXXXX

@@

(142/150 words)

@@

```{r}
matmet_cap <- paste0(
  #"(A) Conceptual model of the hypothesized relationships between environment,
  #species richness, network metrics and total biomass / biomass stability. ",
  #"Solid and dashed arrows represent respectively direct and indirect effects.
  #",
  #"The blue, green and blue/green dashed arrows being respectively indirect
  #effects going through species richness, network metrics and through both
  #species richness and network metrics.",
  "(A) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
  "Inner borders draw the limits of the hydrographic basins. ",
  "(B) The metaweb. Each trophic species (N = 412) is represented by a node and
  each color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
  "(C) Subset over network variation through time."
)
```

```{r matmet, fig.cap = matmet_cap, cache = FALSE}
myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))

@@

```{r get-data, cache = FALSE}
library(piecewiseSEM)
library(lme4)
library(nlme)

@@

```{r indir-stab, cache = TRUE, results = TRUE}
caption_sem <- paste0(
  "Direct, indirect and total effect of environment, species richness and
  network structure, i.e. connectance and mean trophic level on total biomass
  and its temporal stability. Indirect effects are computed by multiplying the
  path coefficients from the variable predictor to the response variable, here
  biomass stability. Indirect effects are considered as one step from the target
  variable. For exemple, the indirect effect of species richness on
  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
  effect, only the significant direct effects were taken into account. ",
  "Network structure being the indirect effect that went through both avg trophic
  level and connectance and Species richness_Network structure being the
  indirect effect that went through (i) species richness and from (ii) species
  richness to network structure."
)

@@

#### Hat

@@

#### Species and total biomass

>>>>

---
title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, Willem Bonnaffe, Elisa Thebault, Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    toc: false 
    fig_caption: true 
    keep_tex: true
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

@@

- Number of words:
  - Abstract: 142 
  - Main text: 4929

- Number of references: XXX
- Number of figures: 2
- Number of tables: 1
- Number of text boxes: 0

- Coresponding author:
  - Alain Danet
  - UMR 7204 CESCO, BP 61; 45, rue Buffon, 75005 Paris, France
  - alain.danet@mnhn.fr 
  - +33140798134

@@

@@

```{r}
matmet_cap <- paste0(
  #"(A) Conceptual model of the hypothesized relationships between environment,
  #species richness, network metrics and total biomass / biomass stability. ",
  #"Solid and dashed arrows represent respectively direct and indirect effects.
  #",
  #"The blue, green and blue/green dashed arrows being respectively indirect
  #effects going through species richness, network metrics and through both
  #species richness and network metrics.",
  "(A) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
  "Inner borders draw the limits of the hydrographic basins. ",
  "(B) The metaweb. Each trophic species (N = 412) is represented by a node and
  each color represent a species (S = 45). Resource nodes (7) were drawn in grey. ",
  "(C) Subset over network variation through time. The species names
  corresponding to the three digit codes are found in Table SXX."
)
```

```{r matmet, fig.cap = matmet_cap}
myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))

@@

```{r get-data}
library(piecewiseSEM)
library(lme4)
library(nlme)

@@

```{r indir-stab, results = TRUE}
caption_sem <- paste0(
  "Direct, indirect and total effect of environment, species richness and
  network structure, i.e. connectance and mean trophic level on total biomass
  and its temporal stability. Indirect effects are computed by multiplying the
  path coefficients from the variable predictor to the response variable, here
  biomass stability. Indirect effects are considered as one step from the target
  variable. For exemple, the indirect effect of species richness on
  biomass stability via its effect on CVsp is $-0.61$. To compute indirect
  effect, only the significant direct effects were taken into account. ",
  "Network structure being the indirect effect that went through both avg trophic
  level and connectance and Species richness_Network structure being the
  indirect effect that went through (i) species richness and from (ii) species
  richness to network structure."
)

@@

@@
